Elastic Scattering in General Relativistic Ray Tracing for Neutrinos

### 2017-09-06 paper.tex
Add section reference to Deaton thesis citation
Change wording facetious->fictitious

We integrate each ray until we reach a terminal optical depth of
$\tau_{\rm term}$ at the earliest effective emission event $x_e^\alpha$.
The concept of earliest emission event is a facetious construct we use
to allow us to truncate our integration at an event along the ray where any
further additions to the field are negligible due to the large optical depth
between $x_e^\alpha$ and $x_o^\alpha$.
We choose $\tau_{\rm term}=14$ so that $e^{-\tau_{\rm term}}<10^{-6}$,
and we then discard the contribution of $f_{\rm bdry}$
(Eqn.~\ref{eqn:rendering_fbdry}).

@@

\subsection{Idealized Compact Star:
  Testing Gravitational Redshift and Geodesic Curvature}
\label{ssec:test_gravity}
Unfinished: describe and point readers to Asano-Fukuyama test presented
in thesis ~\cite{deat2015-thesis}.
Also compare a few geodesics in Kerr to analytic.
\footnote{TODO: compute some geodesics in Kerr}

>>>>

We integrate each ray until we reach a terminal optical depth of
$\tau_{\rm term}$ at the earliest effective emission event $x_e^\alpha$.
The concept of earliest emission event is a fictitious construct we use
to allow us to truncate our integration at an event along the ray where any
further additions to the field are negligible due to the large optical depth
between $x_e^\alpha$ and $x_o^\alpha$.
We choose $\tau_{\rm term}=14$ so that $e^{-\tau_{\rm term}}<10^{-6}$,
and we then discard the contribution of $f_{\rm bdry}$
(Eqn.~\ref{eqn:rendering_fbdry}).

@@

\subsection{Idealized Compact Star:
  Testing Gravitational Redshift and Geodesic Curvature}
\label{ssec:test_gravity}
Unfinished: describe and point readers to Asano-Fukuyama test presented
in thesis ~\cite[Sec.~4.3.3]{deat2015-thesis}.
Also compare a few geodesics in Kerr to analytic.
\footnote{TODO: compute some geodesics in Kerr}
